\section{Concluding Remarks}

In this Thesis, the researchers developed a potential robot system for corn planting in the Philippines. The researchers also implemented a computer vision to its navigation and control mechanism. The robot system was implemented using the Raspberry Pi and its camera module. Through data gathering and analysis, the researchers are able to show that the corn planting robot system can potentially replace human labor in corn production due to its superior speed in planting corn. 

\section{Contributions}


The interrelated contributions and supplements that have been developed in this Thesis are listed as follows.

\begin{itemize}
  \item the seeding mechanism for planting various kinds of average size seeds; 
	
	\item the remote controlled planting robot with real-time video streaming ; 
	
\end{itemize}


\section{Recommendations}

A larger scale, multiple row corn planting robot system with a boring capability is recommended for large producers of corn as a commercially viable production technique given its superiority in terms of quality, production rate, and return of investment as compared to the conventional corn planting approach.

This report also recommends further work to:

\begin{itemize}
\item	Quantify the environmental factors seen at an actual cornfield
\item	Consider the amount of slip and skewing of the wheels during navigation
\item	Categorize the weight limit in relation to the optimal speed of the robot
\item	Develop an algorithm for further automation
\end{itemize}
\section{Future Prospects}

There are several prospect related in this research that may be extended for further studies. The suggested topics are listed in the following.

\begin{enumerate}
	\item	A Robot System for Rice Planting in the Philippines
\item	Development of a Computer Vision Navigation System for Planting Corn in the Philippines
\item	Multiple Camera Image Processing for Rice Planting Success Monitoring and Navigation
\item	Rice Planting Hover Craft Robot for Paddy Field Farming
\item	Aerial Soil Analysis for Potential Agricultural Farm Lands in the Philippines using Swarm Robots

\end{enumerate}


